Earth_microbiome_MS

### 2019-07-16 Earth_microbiome_MS copy.Rmd
updated

#Create table dispaying the average prevalence of each phyla per sample and the total reads for all phyla in the data frame
plyr::ddply(prevdf, "Phylum", function(df1){cbind(mean(df1$Prevalence),sum(df1$Prevalence))})

@@

>>>>

#Create table dispaying the average prevalence of each phyla per sample and the total reads for all phyla in the data frame
plyr::ddply(prevdf, "Phylum (unfiltered)", function(df1){cbind(mean(df1$Prevalence),sum(df1$Prevalence))})

@@

```{r Prevalence Calculations}
#Calculate the mean prevalence from the prevdf
```

```{r Phyloseq filtering}
#Function is simple and could be an alternative - need to check how it fits into code
#https://rdrr.io/github/vmikk/metagMisc/src/R/phyloseq_filter.R#sym-phyloseq_filter_prevalence

#github_filtered3 <- phyloseq_filter_prevalence(githubdata_phyloseq, prev.trh = 0.05, abund.trh = NULL,
  #threshold_condition = "OR", abund.type = "mean")

#print(github_filtered3)
```
